<<<<<<< HEAD
According to \cite{ReadWrite} there are four approaches for recommendation. The first approach is personalized recommendation which is based on the individual’s past behaviour. The second approach is social recommendation which is based on the past behaviour of similar users. The third approach is item recommendation which is based on the item itself. The last approach is a combination of the all three approaches mentioned above. With these four approaches this section will look at solutions on existing recommendation systems.
=======
According to Alex Iskold \cite{ReadWrite} there are four approaches for recommendation. The first approach is personalized recommendation which is based on the individual’s past behavior. The second approach is social recommendation which is based on the past behavior of similar users. The third approach is item recommendation which is based on the item itself. The last approach is a combination of the all three approaches mentioned above. With these four approaches this section will look at solutions on existing recommendation systems.
>>>>>>> e70bc63bffe9a754971b96f84521093584724957


The four approaches are:

\begin{itemize}
	\item Personalized recommendation - recommend things based on the individual users past behaviour. 
	\item Social recommendation - recommend things based on the past behaviour of similar users. 
	\item Item recommendation - recommend things based on the item itself.
	\item A combination of the first three approaches.
\end{itemize}

\subsection{Solutions}
\label{Solutions}
\relinput{Solutions}

\subsection{Overview}
\label{SolutionOverview}
\relinput{SolutionOverview}