According to Alex Iskold, from readwrite.com, there are four approaches for recommendation. The first approach is personalized recommendation which is based on the individual’s past behavior. The second approach is social recommendation which is based on the past behavior of similar users. The third approach is item recommendation which is based on the item itself. The last approach is a combination of the all three approaches mentioned above. With these four approaches this section will look at solutions on existing recommendation systems.

The four approaches are:

\begin{itemize}
	\item Personalized recommendation - recommend things based on the individual’s past behavior. 
	\item Social recommendation - recommend things based on the past behavior  of similar users. 
	\item Item recommendation - recommend things based on the item itself.
	\item A combination of the three approaches.
\end{itemize}

\subsection{Solutions}
\textbf{Amazon}

Amazon is the world’s largest online retailer. It started as an online bookstore but then it soon got every kind of things like movies, electronics, clothes.

Amazon system uses the combination of the three approaches. Which means the system is based on individual behavior, and either the item itself or behavior of similiar users. Amazon have a “what other customer also bought” under the item you are viewing, which is a social and personalized recommendation. A customer reviews is also possible to be view for the item, where the specific customer is available to rate and comment on the item. And based on the reviews it shows the top 3 similiar statements. Amazon gives you other recommendation based on what your history, which is personalized recommendation

\textbf{YouTube}

YouTube is a popular video sharing website which is under control by Google. YouTube system uses the personalized recommendation. YouTube takes your history, and other activity on the site, to give you recommendations, on which it gives recommendations for channels and videos. So basically whatever video you click on will be placed in your personal history list and based on that it will give you some recommendation.

The problem with YouTube is that even if you only watched one second of a certain video, it will be included in the recommendations to come. Unwanted videos can easily be recommended because of this. Channels also gets recommended even after only watching a single video from the channel.

\textbf{IMDB}

Internet Movie Database(IMDB) is database with old to new movies. It gives information about new movie releases and you can be able to watch trailers from the movies before you decide to watch it. IMDB is a kind of  personalized recommendation and social recommendation system. The recommendation system goes by the image X

It also has some based on what you’ve previously seen and rated. The system is to a certain degree, flawed. Despite being sort of a social recommendation, because it is based on what other people have previously seen, there is no friend list or similar, so there is no control regarding what people these social recommendations is based on. The personalized recommendations also has some flaws. As the project groups members tried seeing what it would generate, as a member and not a member of the site, it gave the same recommendations, and showed movies that have already been seen and rated.

\textbf{LinkedIn}

LinkedIn is a social networking website for professional occupations. It is way for people to find, and be found, for projects and/or work based on ones skills, previous experience, and descriptions from other users. It uses text analysis to find certain keywords, like “trustworthy” or “dedicated”, to highlight a person's abilities. LinkedIn also has a “apply from LinkedIn” button, where users can apply for a position in a company, through their LinkedIn profile. 

The system is based on item recommendation, as it is the descriptions, skills, and keywords extracted about the user, that is used for the recommendation. When the user itself search for a person or a company that will be a personalized recommendation. The system could also be some of hybrid recommendation system There can be some problems, if someone begins to write wrong descriptions about another user, both if it intentionally better or worse than it in reality is.

\subsection{Overview}
The most common recommendation type between the four existing solutions is the personalized kind of recommendations. This is followed by the social recommendation type. Item recommendation is visible on some of the solutions, but is less used compared to the other recommendation types.

Personalized and social recommendations seems to fit into collaborative filtering, while item recommendations falls into content-based filtering recommender systems. To cover all possibilities, a hybrid recommendations seems to be the best option, considering Amazon’s success with this kind of recommendation system.

It seems like the personalized and social recommendations is the most important, considering what this project is aiming for. Item recommendation is based solely on data regarding a specific item, rather than a recommendation based on the person's interests, past behavior, and similarities with other people. This will be further investigated in the survey section to find out what people weigh the most, when they receive new media they might consume, or find themselves.