This section looks back upon the problem formulation which were made based on the problem analysis, and tries to answer it based on the design, development, and generally the content which has been worked with during the project. The requirements which were created for product is also looked, to see if it fulfills it.

\textit{How can you construct a hybrid recommendation algorithm, based on collaborative filtering and content-based recommendation, to support recommendations across media?}

The hybrid recommendation algorithm have been constructed using collaborative and content-based filtering by applying the pearson correlation coefficient and the cosine distance between vectors. Pearson compares users by looking at their shared consumed media, finding users who is alike in their taste, and recommends other media they’ve rated high. By utilizing vector representation for all media and users, the cosine distance calculation compares a user with media by their vectors, where each corresponding spot in the vectors is for the same genre, or associated person. The media vector is binary, indicating if they have something or not. The user can alter their vector by rating media, putting more weight on things they like.

Especially the collaborative part of the algorithm can, theoretically, produce recommendation across different kinds of media, since it only looks at ratings. As long as pearson evaluates them to be similar for any media, the collaborative algorithm can easily generates recommendations across media types. This also means it can have a good serendipity, which is when the user is recommended something they necessarily didn’t know they wanted. The content-based is less strong in this aspect, and is more strong in generating recommendation corresponding to the media type the user has in their medialist. The next step would be to do user tests in the form of a beta test, since the collaborative algorithm cannot be properly tested on randomly generated data.

\textit{How can you present media data to the user, through the graphical user interface?}

It was decided early on that a website solution were the most logical way to construct this system, since it made sense to have the users in the same environment. Having a central site for it could also help support further work with potential social networking. This can include having the friendlies feature implemented, comments, forums, etc. Also, since it would have to communicate with a media database most of the time. For this purpose, ASP.NET was chosen to contruct the solution, using both C\#, which was a requirement for the product, and HTML/CSS. 

The graphical user interface(GUI) was initially designed using a paper and slide presentation prototype, which is the foundation for how the GUI eventually ended up looking. The overall design of GUI have not changed much since the initial prototypes. Some elements have been changed though, some have been removed, and theory regarding color have also been applied. The media is presented in similar sized containers with the title and a cover image, if available, for the user to identify the media item. The medialist for each user also shows the rating they’ve given to the media in the some of stars. The designing process of the GUI could have been much more detailed, involving more theory from the interactive design course \cite{DEBBook}, but it was within the goals of this project.

\subsubsection{Product Requirements}

The functional requirements have all been followed for the system. The prototype generates recommendations based on a hybrid system, have a GUI which is targeted towards the defined target audience, can easily run on a desktop PC, and on most popular internet browsers. The GUI could have used more user involvement during the design, like showcasing the prototypes to potential users of the system. A rating system was also implemented, which allows to users to rate any media on a scale from 0 to 10.

The solution goals have also mostly been fulfilled during the project. The two forms of recommendations both had certain disadvantages, which made them on their own weak as a recommendation system. Therefore a hybrid of the two were made, to try and counter these weaknesses. Like previously described, it is possible for media across media type to be recommended, especially with the collaborative algorithm. 

One thing which were not fully implemented is to take into account where the recommendation originates from. The idea was that media recommended through friends would receive a boost, and gain an advantage. The structure for this, including a friends list attribute for users, controler, and website tab, have been made, but not implemented. It had a lowered priority, and it was not possible to make time for it in the end. 

Users can alter the recommendation process by how they rate the media. Different ratings will result in different coefficients from the collaborative algorithm, and extraction of recommendations from different users. As long as the users ratings is similar to the ratings of other users, on the same pieces of media, a good coefficient will be generated. The extraction also doesn’t care what kind of media is being recommended, as long as they’ve been rated high. This allows for serendipity. Ratings also have an effect on the vector representation of the user, altering it to their taste, changing the coefficients made with the content-based algorithm. If the user rates a media low, the corresponding elements in the users vector will have their weight subtracted. The same happens if the media item receives a high rating, except the elements in the user vector will have weight added instead.