\chapter{Interview Questions}
May we record the conversation?
What is your age and work?\\

User rights, how much private information are you okay with being stored at a company (such as. Google) and which parts should be publicly available (eg. Facebook)?
\begin{enumerate}
\item Contact information: Name, address
\item Personal information, age, likes / dislikes, email
\item Very personal information; Chat, emails, photos
\end{enumerate}
 
What entertainment media do you use regularly? (such as. movies / games / books?)\\
 
How do you find information about movies? Are you satisfied with their solution?\\ Can the solution give you good recommendations?\\
How do you find information about games? Are you satisfied with their solution? Can the solution give you good recommendations?\\
How do you find information about books? Are you satisfied with their solution? Can the solution give you good recommendations?\\
 
Do your friends recommend you new entertainment media? And what media do they recommend you?\\
Do you get useful recommendations from other sources?\\
Do your friends music-/movie-/book-taste affect what you see / hear? Why?\\

We intend to create a website that contains several popular media. On the website you make a user profile, where you enter the movies / games / books you have seen. Based on your user profile it gives you a good and accurate recommendation for new movies / games / books.\\

What do you think about such a solution / website? Would you use it?\\

What other features would you like to see on the site? (such as. friendlist, friend recommendations etc? Other media?)\\

